%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Durgesh Nandan} \\ \vspace{1pt}
    \small +44 7776071886 $|$ Birmingham, United Kingdom \\ \href{mailto:durgnan45@gmail.com}{\underline{durgnan45@gmail.com}} $|$ \href{https://durgnan.github.io}{\underline{Portfolio}} $|$ 
    \href{https://www.linkedin.com/in/durgesh-nandan-75a80b140}{\underline{LinkedIn}} $|$
    \href{https://github.com/durgnan}{\underline{Github}} $|$
    \href{https://leetcode.com/durgnan/}{\underline{Leetcode}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Birmingham}{Birmingham, UK}
      {Master of Science in Advanced Computer Science}{Sept. 2023 -- Sept. 2024}
      \resumeSubSubheading
        {Modules: HCI, Dependable and Distributed Systems, Algorithms, Mobile Computing, Computer Vision}{}
    \resumeSubheading
      {Visvesvaraya Technological University}{Belagavi, IN}
      {Bachelor of Engineering in Computer Science and Engineering}{Aug. 2016 -- Aug. 2020}
      \resumeSubSubheading
        {Significant Modules: Data Structures, UNIX, OOPS Java, DBMS, Machine Learning, Big Data, Python Programming}{}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Developer}{June 2023 -- Aug. 2023}
      {Quantiphi}{Bengaluru, IN}
      \resumeItemListStart
        \resumeItem{Designed and engineered an \textbf{RDP (Remote Desktop)} service catering to \textbf{Nvidia} and \textbf{ICI} team requirements, facilitating remote machine management in geographically isolated client locations across 6 continents.}
        \resumeItem{Introduced \textbf{AWS Services} (e.g. API Gateway, IOT Core, OpenSSH) and the \textbf{MEAN} Stack for the development of this solution.}
        \resumeItem{Notably, Completed the project ahead of schedule, allowing for a buffer of approximately two months for thorough multi-stage testing and any ad-hoc modifications.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Full Stack Developer}{Apr. 2022 -- May 2023}
      {AXIO Finance}{Bengaluru, IN}
      \resumeItemListStart
        \resumeItem{Spearheaded the design and development of the \textbf{Tata Pay Later Front-end}, \textbf{managing traffic} due to a \textbf{large customer base.}}
        \resumeItem{Implemented significant contributions to the \textbf{UI/UX} and feature enhancements for \textbf{Amazon Pay Later/AXIO} to maximise user engagement by \textbf{20\%}.}
        \resumeItem{Led the \textbf{re-branding} efforts for the Front-end during the transition from \textbf{Capital Float to AXIO.}}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{July 2020 -- Apr. 2022}
      {Synamedia}{Bengaluru, IN}
      \resumeItemListStart
        \resumeItem{Created, developed, and rigorously tested an \textbf{Automatic Notice and Takedown System} aimed at identifying and addressing pirated content across OTT, DTH, and other platforms. This involved sending legal notices in stages of escalation for persistent offenders.}
        \resumeItem{Developed and tested a comprehensive product from the ground up, utilizing \textbf{MERN/MEAN Stack.}}
        \resumeItem{Developed the back-end server and \textbf{REST APIs}, leveraging \textbf{NodeJS} and \textbf{ExpressJS}, while maintaining API documentation through \textbf{Swagger.}}
        \resumeItem{Employed \textbf{Docker} for containerizing full-stack applications, ensuring swift builds and cloud deployment.}
        \resumeItem{Transformed wire-frames and prototypes into visually appealing and user-friendly web applications.}
        \resumeItem{Executed rigorous multi-stage testing encompassing diverse scenarios, utilizing test beds and stubs, and organised test documents within \textbf{Confluence.}}
        \resumeItem{Gathered and comprehended business requirements from clients and colleagues, proceeding to design, develop, and maintain versions and releases.}
      \resumeItemListEnd

    \resumeSubheading
      {Trainee}{Jan. 2020 -- July. 2020}
      {RoadMetrics}{Bengaluru, IN}
      \resumeItemListStart
        \resumeItem{Facilitated to the development of a road assessment platform for government entities and city councils, resulting in a \textbf{50\%} increase in customer acquisition. Played key role in creating a navigation app for individual consumers, which garnered over \textbf{1,000 downloads} and allowed users to select routes based on \textbf{optimal road conditions.}}
        \resumeItem{Designed and deployed modules in multiple technologies, including UI/UX design, microservices, and APIs, utilizing AWS Lambda, S3, RDS, Android Application Development, Tensorflow, WebStack, Python} Modules, and Single Page Applications with the \textbf{MEAN} stack.
        \resumeItem{Conducted application testing to identify and address technical problems such as \textbf{ANR} (Application Not Responding) issues and crashes.}
        \resumeItem{Assumed responsibility for release management on \textbf{Google Play Store} and the ongoing maintenance of cloud infrastructure.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Orca} $|$ \emph{Mongo DB, Express JS, React, NodeJS, AWS, Google Analytics}}{}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{Analytics Website} as a personal project that can identify and address pirated content across OTT, Telegram, and other social media sources.}
            \resumeItem{Generates trend graphs and other analytical metrics for users to analyse and create report.}
            \resumeItem{Implemented an experimental feature enabling the scheduling of cron jobs to send routine emails. Initially designed the email content in HTML on the server, subsequently parsing and delivering.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{MedApp} $|$ \emph{Java, Android, AWS, Firebase, GCP}}{}
          \resumeItemListStart
            \resumeItem{Developed a mobile application enabling victims and nearby citizens to send emergency alarm messages swiftly.}
            \resumeItem{Implemented real-time location tracking to identify the nearest healthcare providers, including ambulances.}
            \resumeItem{Enabled notifications to be sent to nearby healthcare workers, requesting assistance during emergencies.}
            \resumeItem{Included a feature offering first aid tips for immediate support during crisis situations.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C, JavaScript, HTML5, CSS3, Typescript, XML, SCSS, LESS} \\
     \textbf{Frameworks}{: React, Angular, ExpressJS, Node.js, MEAN, MERN, Flask, Android, Material-UI, REST API, Redux} \\
     \textbf{Databases}{: MySQL, Oracle 11G, SQLite, MongoDB, DynamoDB, Redshift, PostgreSQL, Cassandra} \\
     \textbf{Cloud}{: Google Cloud Platform, AWS, Firebase} \\
     \textbf{Developer Tools}{: Docker, Kubernetes, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Control System, Documentations and UI Wire-framing}{: Git, Jenkins, Jira, Confluence, Asana, Zeplin, Figma, Adobe XD, Sketch} \\
     \textbf{OS}{: Windows, Linux(RedHat, CentOS), macOS} \\
     \textbf{Miscellaneous}{: Public Speaking, Communication, Problem Solving, Leadership, Time Management, Conflict Resolution }
    }}
 \end{itemize}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Finalist, TechGig Code Gladiators 2021:}{ Advanced to the final round of the event, earning a spot in the \textbf{top 100} contenders from a pool of \textbf{400,000 participants.}} \\
     \textbf{Winner, Smart India Hackathon 2020:}{ Secured victory in the Smart India Hackathon 2020 - Software Edition, emerging as the winner among more than \textbf{35,000} participating teams in the \textbf{Government of India} organised three-day hackathon.} \\
     \textbf{3rd/100, Google I/O Extended AppDev Hackathon 2018:}{ Achieved a notable \textbf{third-place} ranking among \textbf{100 teams} at the 2018 Google I/O Extended AppDev Hackathon.} \\
     \textbf{HackerRank:}{ Resolved more than \textbf{100 problems} on HackerRank across multiple programming languages, while also achieving \textbf{gold badges} through participation in competitions and practice.} \\
    }}
 \end{itemize}

%-----------Certifications-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{MERN Specialisation:}{ Hong Kong University of Science and Technology(Coursera).} \\
     \textbf{AWS Fundamentals:}{ Coursera.} \\
     \textbf{MEAN Specialisation:}{ Udemy.} \\
     \textbf{Python:}{ University of Michigan(Coursera).} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
